---
title: "Making Datapackage with DataPackageR"
author: "Thomas Van Hoey"
date: "1/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Steps described in:

* [](https://ropensci.org/blog/2018/09/18/datapackager/)
* [](https://github.com/ropensci/DataPackageR)

On the why:

* [](https://grasshoppermouse.github.io/2017/10/18/put-your-data-in-an-r-package/)

Other methods:

* [](https://www.erikhoward.net/how-to-create-an-r-data-package/)
* [](http://www.clayford.net/statistics/creating-an-r-data-package/)

# Set up
```{r}
library(DataPackageR)
library(here)
library(tidyverse)
```

# Variables

```{r}
PATH <- here()
PACKAGENAME <- "CHIDEOD" #Chinese Ideophone Database R
```


# Getting data from osfr

```{r}
library(osfr)

cr_project <- osf_retrieve_node("kpwgf") # OSF Chinese Ideophone Database
cr_project %>%
  osf_ls_files() %>%
  filter(str_detect(name, "rds")) %>%
  osf_download(overwrite = TRUE)
```

read in data as df
```{r}
df <- read_rds("chideod.rds")
df
```



# Create a data package directory structure.

```{r}
datapackage_skeleton(name = PACKAGENAME,
                     path = PATH,
                     force = TRUE)
```

# Add raw data to the package.
```{r}
# NOW WITH RDS
# write our raw data to a csv 
#write.csv(x = df,file = file.path(PATH, "chideod.csv"), row.names = FALSE)

# write raw data to rds
write_csv(df, file.path(PATH, "chideod.csv"))

# this works because we called datapackage_skeleton() first.
use_raw_dataset(file.path(PATH, "chideod.csv"))
```


# Add a data processing script.

```{r}
use_processing_script(file = "chinese_database.Rmd",
                      author = "Thomas Van Hoey",
                      title = "Process OSF repository data into datapackage")
```


# Edit your processing script (the Rmd file)


```
---
title: Process OSF repository data into datapackage
author: Thomas Van Hoey
date:  8 July, 2019
output_format: html_document
---

```{r}
chideod <- df
```

```

# Let DataPackageR know about the data objects to store in the package.

```{r}
use_data_object("chideod")
```

# Build the package (for the first time).

```{r}
options("DataPackageR_interact" = FALSE)
package_build(packageName = file.path(PATH, "CHIDEOD"),
              install = FALSE)
```

# Next edit the data set documentation.
File can be found under `data-raw`, the `documentation.R` file

>This is standard roxygen markup. You can use roxygen or markdown style comments. You should 
* describe your data set, 
* where it comes from, 
* the columns of the data (if applicable), and 
* any other information that can help a user make good use of and understand the data set. 
We’ll fill this in and save the resulting file.

```
#' CHIDEOD
#' A data package for CHIDEOD.
#' @docType package
#' @aliases CHIDEOD-package
#' @title CHIDEOD -- The Chinese Ideophone Database
#' @name CHIDEOD
#' @description AThis package contains the Chinese Ideophone Database CHIDEOD.
#' @details Use \code{data(package='CHIDEOD')$results[, 3]} to see a list of available data sets in this data package
#'     and/or DataPackageR::load_all
#' _datasets() to load them.
#' @seealso
#' \link{chideod}
NULL



#' Detailed description of the data
#' @name chideod
#' @docType data
#' @title The Chinese Ideophone Database (CHIDEOD)
#' @format a \code{tbl_df} containing the following fields:
#' \describe{
#' \item{traditional}{}
#' \item{simplified}{}
#' \item{pinyintone}{}
#' \item{pinyinnum}{}
#' \item{pinyinnone}{}
#' \item{HYDCD}{}
#' \item{zdic}{}
#' \item{Kroll}{}
#' \item{MC}{}
#' \item{OC}{}
#' \item{radsup}{}
#' \item{S1}{}
#' \item{S2}{}
#' \item{S3}{}
#' \item{S4}{}
#' \item{T1}{}
#' \item{T2}{}
#' \item{T3}{}
#' \item{T4}{}
#' \item{morphology}{}
#' \item{S1.charfreq}{}
#' \item{S2.charfreq}{}
#' \item{S3.charfreq}{}
#' \item{S4.charfreq}{}
#' \item{S1.famfreq}{}
#' \item{S2.famfreq}{}
#' \item{S3.famfreq}{}
#' \item{S4.famfreq}{}
#' \item{S1.sem}{}
#' \item{S2.sem}{}
#' \item{S3.sem}{}
#' \item{S4.sem}{}
#' \item{S1.semfreq}{}
#' \item{S2.semfreq}{}
#' \item{S3.semfreq}{}
#' \item{S4.semfreq}{}
#' \item{S1.semfam}{}
#' \item{S2.semfam}{}
#' \item{S3.semfam}{}
#' \item{S4.semfam}{}
#' \item{S1.phon}{}
#' \item{S2.phon}{}
#' \item{S3.phon}{}
#' \item{S4.phon}{}
#' \item{S1.phonfreq}{}
#' \item{S2.phonfreq}{}
#' \item{S3.phonfreq}{}
#' \item{S4.phonfreq}{}
#' \item{S1.phonfam}{}
#' \item{S2.phonfam}{}
#' \item{S3.phonfam}{}
#' \item{S4.phonfam}{}
#' \item{sensorymod}{}
#' \item{variant}{}
#' \item{note}{}
#' \item{datasource}{}
#' \item{stage}{}
#' \item{ASBC.dp}{}
#' \item{ASBC.philosophy}{}
#' \item{ASBC.literature}{}
#' \item{ASBC.life}{}
#' \item{ASBC.society}{}
#' \item{ASBC.science}{}
#' \item{ASBC.art}{}
#' }
#' @source The data comes from https://osf.io/kpwg.
#' 
#' 
#' @seealso
#' \link{CHIDEOD}
NULL

```

Next, run `document()` in the next chunk

```{r}
# ensure we run document() from the DataPackageR namespace and not document() from roxygen or devtools.
package_path <- file.path(PATH, PACKAGENAME)
DataPackageR::document(package_path)
```

# Iterate…

## the DESCRIPTION file

```
Package: CHIDEOD
Title: Data package containing the Chinese Ideophone Database
Version: 0.8
Authors@R: 
    person(given = "Thomas",
           family = "Van Hoey",
           role = c("aut", "cre"),
           email = "thomas_van_hoey@hotmail.com")
Description: This package contains the contents of the Chinese Ideophone Database CHIDEOD.
License: GNU General Public License v2.0
Encoding: UTF-8
LazyData: true
DataVersion: 0.5.0
Roxygen: list(markdown = TRUE)
Date: 2019-07-08
Suggests: 
    knitr,
    rmarkdown
VignetteBuilder: knitr
RoxygenNote: 6.1.1
```

```{r}
# ensure we run document() from the DataPackageR namespace and not document() from roxygen or devtools.
package_path <- file.path(PATH, PACKAGENAME)
DataPackageR::document(package_path)
```




# A final build.

```{r}
package_build(file.path(PATH, PACKAGENAME))
```

# Installing test

```{r}
library(devtools)
install_github("simazhi/chinese_ideophone_database/CHIDEOD")
#detach(package:devtools,unload = TRUE)
#install.packages("CHIDEOD_0.8.tar.gz", type = "source")

library(CHIDEOD)

data(package = "CHIDEOD")

chideod # so it worked, the data is now here
```


