---
title: "postprocessing"
author: "Thomas Van Hoey"
date: "10/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
library(glue)
```


```{r}
file <- read_csv(here("finder.results_20191004.csv"), col_names = FALSE) %>%
  rename(class = X1,
         article.no = X2,
         line = X3)  
```


```{r}
words <- read_csv("list.of.traditional.ideophones.csv") 
words <- words %>%
  mutate(traditional = case_when(
    nchar(traditional) < 2 ~ str_replace(traditional, "(.)", " \\1_"),
    TRUE ~ traditional
  )) 
search.expressions <- pull(words)
search.2 <- glue_collapse(search.expressions, sep = "|")
#search.2
```



```{r}
file %>%
  mutate(ideo = str_extract_all(line,search.2)) %>%
  #select(t) %>%
  unnest(ideo) -> file.ideo

```

```{r}
file.ideo.norm <- file.ideo %>%
  mutate(ideo = str_replace(ideo, "_", ""),
         ideo = str_squish(ideo))

write_csv(file.ideo.norm, "ASBC_unnested.csv", col_names = TRUE)
```


# Start from here

```{r}
file.ideo.norm <- read_csv("ASBC_unnested.csv")

skimr::skim(file.ideo.norm)

file.ideo.norm %>%
  count(class)

file.ideo.norm %>%
  count(ideo, sort = TRUE)
```

Based on the result of `file.ideo %>% count(ideo, sort = TRUE)` it is maybe best to scrutinize a number of the results.

# 得

word | n in ASBC | datasource
---- | -------- | ---
得	| 13992 | Li

```{r}
file.ideo.norm %>% filter(ideo == "得") %>%
  mutate(de.category = str_extract_all(line, "\\b得_\\w+\\b")) %>%
  unnest(de.category) %>%
  count(de.category, sort = TRUE) 
```

```{r}
file.ideo.norm %>% filter(ideo == "得") %>%
  mutate(de.category = str_extract_all(line, "\\b得_\\w+\\b")) %>%
  unnest(de.category) 
```

Conclusion: based on its definition in CHIDEOD (from Li 2007) and its multiple grammatical functions, it is better if 得 is excluded from CHIDEOD.

# Sentence final particles

word | n in ASBC | datasource | tag
---- | --------			| --- | ---
呢	| 7798			| Wang, Li | T [particle]
啊	| 4975			| Gong, Li | I & T [interjection, particle]
吧	| 3581			| Wang, Gong, Li | T
當	| 	3513			| Gong, Li | D, I, Na, Nes, P, VA, VC, VE, VG, VH, VJ
台		| 2746			| Li | Na, Nc, Nf
呀		| 2266	| Wang, Gong, Li | D[is okay] & T[not okay]
往往	| 1502	|	Kroll | D[maybe grammaticalized?]
突然	| 1415	| HYDCD | D & V [both grammaticalized?]
喔	 | 1087	 | Gong | I, T 
消息	 | 1074	| Kroll | Na[because used to be verbal, now noun 'news']		
好好	 | 	991	| Shijing | VH, D[both grammaticalized?]
顯然	 | 	928	| HYDCD | D [okay]
紛紛	 | 	917		 |  Kroll, Tang 	 | D [gramm/ okay]
拍		 | 813 | Gong | D, Na, Nv, VC [not ideophone?]
種種		 | 795 | HYDCD | Neqa, Nf, VC [not ideophone?]
彷彿	 | 	778	 | Kroll | D, VG [grammaticalized?]
嗯		 | 738	 | Gong | I 
漸漸		 | 732	 | Shijing | D [grammaticalized]
號		 | 688	 | Gong | Na, Nc, Nf, VG
哦 |	668 | Li | I, T
忽然 |	658	| Tang | D [okay?]
念 |	634	| Li | Na, Nv, VB, VC, VJ
空 |	620	| Gong | D, Na, Nb, Nc, Nv, VC,VH, VHC
模糊 | 	518	| Kroll | Nv, VH [ok/grammaticalized]
通 |	483	| Li | D, Na, Neqa, Nf, Nv, VA, VC, VCL, VE, VH, VJ
深深 | 	469	| HYDCD | VH [ok/grammaticalized]
東 |	463	| Gong | Nc, Ncd
果然 |	454	| HYDCD | D [ok/grammaticalized]
架	| 414 | 

```{r}
file.ideo.norm %>%
  count(ideo, sort = TRUE) 
```


```{r}
library(CHIDEOR)

search.word <- "實實"

chideod %>%
  filter(traditional == search.word) %>%
  pull(HYDCD)

chideod %>%
  filter(traditional == search.word) %>%
  pull(Kroll)

chideod %>%
  filter(traditional == search.word) %>%
  select(datasource)
```

```{r}
file.ideo.norm %>% filter(ideo == search.word) %>%
  mutate(de.category = str_extract_all(line, glue("\\b{search.word}_\\w+\\b"))) %>%
  unnest(de.category) -> tag.found
tag.found

tag.found %>%
  count(de.category)

tag.found %>%
  filter(str_detect(de.category, "VC"))
```

# First visualization

```{r}
library(showtext)
showtext_auto()

file.ideo.norm %>%
  count(ideo, sort = TRUE) %>%
  ggplot() +
  geom_bar(aes(reorder(ideo, n), n),
           stat = "identity") +
  coord_flip()
  
```

```{r}
takeouts <- read_csv("post_procssing_filtering.csv") %>%
  filter(takeout == "Y")


file.ideo.norm %>%
  anti_join(takeouts, by = c("ideo" = "word")) %>%
  count(ideo, sort = TRUE) %>%
  ggplot() +
  geom_bar(aes(reorder(ideo, n), n),
           stat = "identity") +
  coord_flip()
  
```

Okay, so a Zipf curve is totally what we would expect in both cases.
The more frequent ones are also probably more grammaticalized even though they can still be integrated in the verbal complex.


# Basic statistics

```{r}
file.ideo.norm %>% 
  anti_join(takeouts, by = c("ideo" = "word")) %>%
  distinct() -> curated.ideos.ASBC
```


## Gries's dispersion

So now we have `r nrow(curated.ideos.ASBC)` observations, I think it's enough.

So now we need to
* count number of observations per class
* turn into wider format
* ~~rename the categories~~
* make sure the order is the same as the one of totals
```{r}
ASBC.ideo.obs <- curated.ideos.ASBC %>%
  count(class, ideo) %>%
  arrange(ideo) %>%
  pivot_wider(names_from = class,
              values_from = n) 
ASBC.ideo.obs
```

 
Total frequencies (words)
哲學	1129554			
文學	2244729			
生活	2253121			
社會	3636877			
科學	1132392			
藝術	849182	
```{r}
totals.abs <- tribble(
  ~ 哲學, ~文學, ~生活, ~社會, ~科學, ~藝術,
  1129554, 2244729, 2253121, 3636877, 1132392, 849182	
)
totals.abs
ASBC4.total.exp <- prop.table(totals.abs)
ASBC4.total.exp
```


```{r}
ASBC.ideo.obs %>%
  replace(is.na(.), 0) %>% # replace the NAs with 0
  janitor::adorn_percentages() %>% # replaces prop.table
  mutate(literature = abs(文學 - ASBC4.total.exp$文學),
         life = abs(生活 - ASBC4.total.exp$生活),
         society = abs(社會 - ASBC4.total.exp$社會),
         science = abs(科學 - ASBC4.total.exp$科學),
         philosophy = abs(哲學 - ASBC4.total.exp$哲學),
         art = abs(藝術 - ASBC4.total.exp$藝術)) %>%
  mutate(total = literature + life + society + science + philosophy + art) %>% # totals of the newly computed values
  mutate(dp = total / 2) %>%
  as_tibble() %>%
  select(-literature, -life, -society, -science, -philosophy, -art, -total) -> ASBC.ideo.dispersion

ASBC.ideo.dispersion %>%
  select(ideo, dp, everything()) %>%
  arrange(dp) %>%
  left_join(ASBC.ideo.obs, by = c("ideo")) -> ASBC.ideo.dispersion.raw
ASBC.ideo.dispersion.raw

```


So what is the relation between dispersion and raw frequency?

```{r}
library(showtext)
showtext_auto()

ASBC.ideo.dispersion.raw %>%
  replace(is.na(.), 0) %>%
  mutate(rawfreq = reduce(select(., ends_with(".y")), `+`)) %>% # summarize over raw frequencies
  ggplot(aes(dp, rawfreq)) +
  geom_point() +
  gghighlight::gghighlight(rawfreq > 250, label_key = ideo) +
  theme_bw() 
```

# Frequencies

```{r}
e <- ecdf(ASBC.ideo.dispersion.raw$dp)

ASBC.ideo.dispersion.raw %>%
  ggplot(aes(dp)) +
  #geom_histogram() +
  stat_ecdf() +
  theme_bw() +
  #geom_label(aes(x = e(0.25), y = 0.25),
  #           label = e(0.25))
  geom_point(aes(x = e(0.75), y = e(0.75))) +
  geom_point(aes(x = e(0.50), y = e(0.50))) +
  geom_point(aes(x = 0.33, y = 0.25))

```


# ABB?

```{r}
curated.ideos.ASBC %>%
  mutate(ABB = str_extract(line, glue("\\b\\w+{ideo}\\w+\\b"))) %>%
  drop_na(ABB) %>%
  mutate(collocate = str_extract(ABB, glue(".+(?={ideo})")))-> ASBC.ABBs

ASBC.ABBs 
  

ASBC.ABBs %>% count(ideo, sort = TRUE)
```

```{r}
ASBC.ABBs %>% count(ideo, ABB, collocate) %>%
  arrange(ideo)
```

```{r}
ASBC.ABBs %>%
  filter(str_detect(ABB, "黃")) %>%
  count(ABB, collocate)
```

Critique on formal studies that typically take only one thing into account.
This is really fun with colors! 
黑|白|紅|黃|綠

```{r}
ASBC.ABBs %>%
  filter(str_detect(ABB, "油")) %>%
  count(ABB, collocate)
```

So yes, unit status, but also yes to (partial) compositionality.
Against ABB!

# Tags

```{r}
curated.ideos.ASBC %>%
  mutate(expression = str_extract(line, glue("\\b\\w*{ideo}\\w+\\b")),
         tag = str_replace(expression, ".+_", "")) %>%
  count(tag, sort = TRUE)
  

```



# Possible further ideas

Looking at constructions and their association measures









