---
title: "revision"
author: "Thomas Van Hoey"
date: "12/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(CHIDEOD)
library(tidyverse)
library(here)
library(data.table)
```



# Step 1
check 
* note (for interjection),
* Kroll (for spelling mistakes)


```{r}
chideod %>%
  select(traditional, pinyinnum, note, HYDCD, zdic, Kroll) %>%
  mutate(meaning = "") %>% 
  arrange(desc(note, traditional)) %>%
  distinct() #%>%
  #write_csv(here::here("revision", "interjection.csv"))
```

Ok, I have manually checked this.

```{r}
krollupdated <- read_csv(here("revision",
                              "interjection20191209.csv"))
krollupdated %>%
  select(traditional, note, Kroll) %>%
  distinct() -> kroll.note.updated
kroll.note.updated
```


# Step 2

Get all zdic definitions (a lot were "notchecked")

* zdic

I gathered this in a separate script.

```{r}
zdics <- read_csv(here("zdic", "zdicwords_20191213.csv"), col_names = FALSE) %>%
  rename(number = X1,
         def = X2,
         ideo = X3)
zdics %>%
  unite(definition, number, def, 
         sep = " ") %>%
  group_by(ideo) %>%
  summarise(definition = str_c(definition, 
                               collapse = "; ")) %>%
  mutate(definition = str_replace_all(definition, "\r|\n|\t", " ")) %>%
  rename(zdic2 = definition) %>%
  distinct() -> zdic.updated
zdic.updated
```


OK.


# Step 3

merge into old table

* Kroll
* note
* zdic

```{r}
chideod %>%
  select(-Kroll, -note) %>%
  left_join(kroll.note.updated, by = "traditional") %>%
  left_join(zdic.updated, by = c("traditional" = "ideo")) %>%
  mutate(zdic = case_when(
    is.na(zdic2) == FALSE ~ zdic2,
    TRUE ~ zdic
  )) %>%
  select(-zdic2) %>%
  distinct() -> chideod.kroll.note.zdic
```

* interjection column

```{r}
chideod.kroll.note.zdic %>%
  mutate(interjection = case_when(
    str_detect(note, "interjection") ~ "interjection",
    TRUE ~ "notinterjection")) -> chideod.interjection

# chideod.interjection  %>%
#   count(traditional, interjection) %>%
#   count(interjection)
```


# Step 4

## Sensory imagery

* tidy sensory imagery
```{r}
chideod.interjection %>%
  separate_rows(sensorymod, 
           sep = "\\+") %>%
  mutate(sensory_imagery = case_when(
    sensorymod == "EVALUATIVE" ~ "EVALUATION",
    sensorymod == "FEELING" ~ "INNER_FEELINGS",
    sensorymod == "INNERFEELINGS" ~ "INNER_FEELINGS",
    sensorymod == "TACTILE" ~ "TEXTURE",
    sensorymod == "WETNESS" ~ "TEXTURE",
    TRUE ~ sensorymod
  )) -> chideod.sensory.imagery


```

This is the step that needs to be merged with the following two sets.

## Middle Chinese in ipa

* ipa of Middle Chinese

get T1 to T4
pivot_longer
connect to baxtesagart dataset
merge together


```{r}
library(baxteRsagaRt)
baxtersagart
```

```{r}
chideod.sensory.imagery %>%
  select(T1:T4, traditional) %>%
  rowid_to_column() %>%
  pivot_longer(cols = starts_with("T", ignore.case = FALSE),
               names_to = "Tval") %>%
  left_join(baxtersagart, by = c("value" = "traditional")) %>%
  select(rowid, Tval, value, MCbaxter, MCipa, OC, traditional)  %>%
  distinct() -> chideod.mc1

chideod.mc1 
 # drop_na(MCbaxter)
```

Function I stole from here for faster unnesting: https://www.johannesbgruber.eu/post/a-faster-unnest/
```{r}
unnest_dt2 <- function(tbl, ...) {

  tbl <- as.data.table(tbl)

  col <- ensyms(...)

  clnms <- syms(setdiff(colnames(tbl), as.character(col)))

  tbl <- as.data.table(tbl)

  tbl <- eval(
    expr(tbl[, lapply(.SD, unlist), by = list(!!!clnms), .SDcols = as.character(col)])
  )
  
  colnames(tbl) <- c(as.character(clnms), as.character(col))

  tbl
}
```



```{r}
chideod.mc1 %>%
  pivot_wider(names_from = Tval,
              values_from = c(MCbaxter:OC)
              ) %>%
  unnest_dt2(MCbaxter_T1, MCbaxter_T2, MCbaxter_T3, MCbaxter_T4,
             MCipa_T1, MCipa_T2, MCipa_T3, MCipa_T4,
             OC_T1, OC_T2, OC_T3, OC_T4) %>% 
  as_tibble() %>%
  #unnest() %>% #tidyr::unnest was really slow, so I used a data.table trick
  mutate(MCbaxter = glue::glue("{MCbaxter_T1}~{MCbaxter_T2}~{MCbaxter_T3}~{MCbaxter_T4}"),
         MCipa = glue::glue("{MCipa_T1}~{MCipa_T2}~{MCipa_T3}~{MCipa_T4}"),
         OCipa = glue::glue("{OC_T1}~{OC_T2}~{OC_T3}~{OC_T4}")) %>%
  mutate(OCipa = str_remove_all(OCipa, "\\*")) %>%
  select(rowid, traditional, MCbaxter, MCipa, OCipa) -> chideod.mc
```

```{r}
chideod.mc %>%
  select(-rowid) %>%
  distinct() %>%
  mutate (nacheck = case_when(
    MCbaxter == "NA~NA~NA~NA" ~ "notfound",
    TRUE ~ "ok"
  )) %>% # okay first take out the multiple options that are 4 NAs
  ungroup() %>%
  mutate(traditional.dup =ifelse(duplicated(traditional) | duplicated(traditional, fromLast = TRUE), "dup","sing")) %>%
  group_by(traditional) %>%
  filter(!(traditional == "dup") & !(nacheck == "notfound")) %>%
  select(-nacheck, -traditional.dup) %>%
  # now we remove excessives NAs for three, two and one syllable words
  mutate(MCbaxter = as.character(MCbaxter),
         MCipa = as.character(MCipa),
         OCipa = as.character(OCipa)) %>%
  mutate(MCbaxter = case_when(
    nchar(traditional) == 1 ~ str_remove(MCbaxter, "~NA~NA~NA$"),
    nchar(traditional) == 2 ~ str_remove(MCbaxter, "~NA~NA$"),
    nchar(traditional) == 3 ~ str_remove(MCbaxter, "~NA$"),
    TRUE ~ MCbaxter
  )) %>%
  mutate(MCipa = case_when(
    nchar(traditional) == 1 ~ str_remove(MCipa, "~NA~NA~NA$"),
    nchar(traditional) == 2 ~ str_remove(MCipa, "~NA~NA$"),
    nchar(traditional) == 3 ~ str_remove(MCipa, "~NA$"),
    TRUE ~ MCipa
  )) %>%
  mutate(OCipa = case_when(
    nchar(traditional) == 1 ~ str_remove(OCipa, "~NA~NA~NA$"),
    nchar(traditional) == 2 ~ str_remove(OCipa, "~NA~NA$"),
    nchar(traditional) == 3 ~ str_remove(OCipa, "~NA$"),
    TRUE ~ OCipa
  )) -> chideod.mc.noduplicates

```

**I think it is important to keep a lot of variation in and uncertainty for the reconstructions.**
It is up to the person that uses CHIDEOD to look at this data and make educated guesses.



## Mandarin ipa

* ipa of Mandarin

python
dragonmapper

from dragonmapper import transcriptions
dragonmapper.transcriptions.pinyin_to_ipa(s)


```{r}
chideod.sensory.imagery %>%
  select(pinyintone) %>%
  pull() %>%
  str_replace_all("~", " ") -> pinyintones
```



```{r}
library(CLD)
cld %>%
  select(C1Pinyin:C4Pinyin) %>%
  pivot_longer(cols = everything(),
               names_to = "cpinyin",
               values_to = "pinyin") -> cld.ipa

cld %>%
  select(C1IPA:C4IPA) %>%
  pivot_longer(cols = everything(),
               names_to = "cipa",
               values_to = "ipa") %>%
  cbind(cld.ipa) %>%
  select(pinyin, ipa) %>%
  distinct() %>%
  drop_na()  -> pinyin.ipa.corr

chideod.sensory.imagery %>%
  select(pinyinnum) %>%
  separate(pinyinnum,
           into = c("s1", "s2", "s3", "s4")) %>%
  stack() %>%
  select(-ind) %>%
  distinct() %>%
  left_join(pinyin.ipa.corr, by = c("values" = "pinyin")) %>%
  mutate(ipanotone = str_remove(ipa, "\\d"),
         valuetonenumber = str_extract(values, "\\d"),
         valuenotone = str_remove(values, "\\d"),
         ipanumber =str_extract(ipa, "\\d")) %>% 
  select(values, valuenotone, valuetonenumber,
         ipa, ipanotone, ipanumber) %>%
  mutate(ipanumber = case_when(
    is.na(ipanumber) ~ valuetonenumber,
    TRUE ~ ipanumber
  ))  -> pinyin.ipa.corr.updated

#write_csv(pinyin.ipa.corr.updated,
#          here("revision", "pinyin.ipa.list.csv"),
#          col_names = TRUE)
```

This we correct

```{r}
pinyin.ipa.corr.updated <- read_csv(here("revision", "pinyin.ipa.list.csv"),
                                    col_names = TRUE) 

pinyin.ipa.corr.updated %>%
  select(values, ipanotone, ipanumber) %>%
  mutate(ipanumber = as.character(ipanumber)) %>%
  mutate(tonenumber = case_when( ipanumber == "1" ~ "55", # tonenumber
      ipanumber == "2" ~ "35",
      ipanumber == "3" ~ "214",
      ipanumber == "4" ~ "51",
      ipanumber == "5" ~ ""),
    toneletter = case_when(ipanumber == "1" ~ "˥",     # toneletter
      ipanumber == "2" ~ "˧˥",
      ipanumber == "3" ~ "˨˩˦",
      ipanumber == "4" ~ "˥˩",
      ipanumber == "5" ~ "")) %>%
  #uniting
  mutate(ipatoneletter = as.character(glue::glue("{ipanotone}{toneletter}")),
         ipatonenumber = as.character(glue::glue("{ipanotone}{tonenumber}"))) %>%
  select(values, ipatoneletter, ipatonenumber) %>%
  rename(pinyin = values) -> pinyin.ipa.corr
```



```{r}
chideod.sensory.imagery %>%
  select(pinyinnum) %>%
  separate(pinyinnum,
           into = c("s1", "s2", "s3", "s4")) %>%
  # adding the ipa
  left_join(pinyin.ipa.corr, by = c("s1" = "pinyin")) %>%
  rename(ipatoneletter1 = ipatoneletter, ipatonenumber1 = ipatonenumber) %>%
  left_join(pinyin.ipa.corr, by = c("s2" = "pinyin")) %>%
  rename(ipatoneletter2 = ipatoneletter, ipatonenumber2 = ipatonenumber) %>%
  left_join(pinyin.ipa.corr, by = c("s3" = "pinyin")) %>%
  rename(ipatoneletter3 = ipatoneletter, ipatonenumber3 = ipatonenumber) %>%
  left_join(pinyin.ipa.corr, by = c("s4" = "pinyin")) %>%
  rename(ipatoneletter4 = ipatoneletter, ipatonenumber4 = ipatonenumber) %>%
  # uniting the columns
  unite(col = ipa_toneletter,
        contains("letter"),
        sep = "~") %>%
  unite(col = ipa_tonenumber,
        contains("number"),
        sep = "~") %>%
  mutate(ipa_toneletter = case_when(
    str_detect(ipa_toneletter, "~NA~NA~NA$") ~ str_remove(ipa_toneletter, "~NA~NA~NA$"),
    str_detect(ipa_toneletter, "~NA~NA$") ~ str_remove(ipa_toneletter, "~NA~NA$"),
    str_detect(ipa_toneletter, "~NA$") ~ str_remove(ipa_toneletter, "~NA$"),
    TRUE ~ ipa_toneletter
    )) %>%
  mutate(ipa_tonenumber = case_when(
    str_detect(ipa_tonenumber, "~NA~NA~NA$") ~ str_remove(ipa_tonenumber, "~NA~NA~NA$"),
    str_detect(ipa_tonenumber, "~NA~NA$") ~ str_remove(ipa_tonenumber, "~NA~NA$"),
    str_detect(ipa_tonenumber, "~NA$") ~ str_remove(ipa_tonenumber, "~NA$"),
    TRUE ~ ipa_tonenumber
  )) -> chideod.ipa.okay


```


## Merging everyhing together

```{r}
chideod.sensory.imagery %>%
  cbind(ipa_toneletter = chideod.ipa.okay$ipa_toneletter) %>%
  cbind(ipa_tonenumber = chideod.ipa.okay$ipa_tonenumber) %>%
  left_join(chideod.mc.noduplicates, by = "traditional") -> chideod.ipas.Mand.MC.OC
```


# Step 5

Turning the different meaning columns into one "definition" column
* Kroll
* HYDCD
* zdic


```{r}
chideod.ipas.Mand.MC.OC %>%
  pivot_longer(cols = c(HYDCD, Kroll, zdic),
               names_to = "test",
               values_to = "definitions") %>%
  select(-test) %>%
  distinct() %>%
  filter(!str_detect(traditional, "呣")) %>%
  select(-MC, -OC, -sensorymod) %>%
  rename(pinyin_tone = pinyintone,
         pinyin_tonenumber = pinyinnum,
         pinyin_without_tone = pinyinnone,
         radical_support = radsup,
         simplified1 = S1,
         simplified2 = S2,
         simplified3 = S3,
         simplified4 = S4,
         traditional1 = T1,
         traditional2 = T2,
         traditional3 = T3,
         traditional4 = T4,
         morphological_template = morphology,
         character1_freq = S1.charfreq,
         character2_freq = S2.charfreq,
         character3_freq = S3.charfreq,
         character4_freq = S4.charfreq,
         character1_family_size = S1.famfreq,
         character2_family_size = S2.famfreq,
         character3_family_size = S3.famfreq,
         character4_family_size = S4.famfreq,
         character1_semantic_radical = S1.sem,
         character2_semantic_radical = S2.sem,
         character3_semantic_radical = S3.sem,
         character4_semantic_radical = S4.sem,
         character1_semantic_radical_freq = S1.semfreq,
         character2_semantic_radical_freq = S2.semfreq,
         character3_semantic_radical_freq = S3.semfreq,
         character4_semantic_radical_freq = S4.semfreq,
         character1_semantic_family_size = S1.semfam,
         character2_semantic_family_size = S2.semfam,
         character3_semantic_family_size = S3.semfam,
         character4_semantic_family_size = S4.semfam,
         character1_phonetic_component = S1.phon,
         character2_phonetic_component = S2.phon,
         character3_phonetic_component = S3.phon,
         character4_phonetic_component = S4.phon,
         character1_phonetic_component_freq = S1.phonfreq,
         character2_phonetic_component_freq = S2.phonfreq,
         character3_phonetic_component_freq = S3.phonfreq,
         character4_phonetic_component_freq = S4.phonfreq,
         character1_phonetic_family_size = S1.phonfam,
         character2_phonetic_family_size = S2.phonfam,
         character3_phonetic_family_size = S3.phonfam,
         character4_phonetic_family_size = S4.phonfam,
         orthograpic_variants = variant,
         data_source = datasource,
         language_stage = stage,
         middle_chinese_baxter = MCbaxter,
         middle_chinese_ipa = MCipa,
         old_chinese_ipa = OCipa
         ) %>%
  select(traditional, simplified, 
         pinyin_tone, pinyin_tonenumber, pinyin_without_tone,
         ipa_toneletter, ipa_tonenumber,
         middle_chinese_baxter, middle_chinese_ipa,
         old_chinese_ipa,
         language_stage, data_source,
         definitions,
         starts_with("simplified"),
         starts_with("traditional"),
         morphological_template,
         radical_support,
         starts_with("character"),
         interjection,
         sensory_imagery,
         everything()
         ) -> chideod.almost.finished # renaming
```

Oh 3th and 4th column needs to be checked
(probably conversion problems at one point)

```{r}
chideod.almost.finished
```


```{r}
cld %>%
  select(S1:S4) %>%
  pivot_longer(everything(), #names_to = "var", 
               values_to = "simp") -> cld.s

cld %>%
  select(C1Frequency:C4Frequency) %>%
  pivot_longer(everything(),
               values_to = "freq") -> cld.frequency

cld %>%
  select(C1FamilySize:C4FamilySize) %>%
    pivot_longer(everything(),
               values_to = "famsize") -> cld.famsize

cld %>%
  select(C1SR:C4SR) %>%
  pivot_longer(everything(),
               values_to = "semrad") -> cld.semrad

cld %>%
  select(C1SRFrequency:C4SRFrequency) %>%
  pivot_longer(everything(),
               values_to = "semfreq") -> cld.semfreq


cld %>%
  select(C1SRFamilySize:C4SRFamilySize) %>%
  pivot_longer(everything(),
               values_to = "semfamsize") -> cld.semfamsize

cld %>%
  select(C1PR:C4PR) %>%
  pivot_longer(everything(),
               values_to = "phon") -> cld.phoneticcomponent

cld %>%
  select(C1PRFrequency:C4PRFrequency) %>%
  pivot_longer(everything(),
               values_to = "phonfreq")  -> cld.phoneticcomponent.freq

cld %>%
  select(C1PRFamilySize:C4PRFamilySize) %>%
  pivot_longer(everything(),
               values_to = "phonfam")  -> cld.phoneticfamily

cld.extracted <-  bind_cols(cld.s, cld.frequency, cld.famsize, 
      cld.semrad, cld.semfreq, cld.semfamsize,
      cld.phoneticcomponent, cld.phoneticcomponent.freq, cld.phoneticfamily) %>%
  distinct()

cld.extracted %>%
  select(-starts_with("name")) %>%
  distinct() %>%
  drop_na() -> cld.extracted.measures

write_csv(cld.extracted.measures, here("interesting_lists", "cld.extractedmeasures.csv"), col_names = TRUE)

cld.extracted.measures
```


```{r}
chideod.almost.finished %>%
  left_join(cld.extracted.measures, by = c("simplified1" = "simp")) %>%
  mutate(character1_freq = freq,
         character1_family_size = famsize,
         character1_semantic_radical = semrad,
         character1_semantic_radical_freq = semfreq,
         character1_semantic_family_size = semfamsize,
         character1_phonetic_component = phon, 
         character1_phonetic_component_freq = phonfreq,
         character1_phonetic_family_size = phonfam) %>%
  select(-freq:-phonfam) %>%
  left_join(cld.extracted.measures, by = c("simplified2" = "simp")) %>%
  mutate(character2_freq = freq,
         character2_family_size = famsize,
         character2_semantic_radical = semrad,
         character2_semantic_radical_freq = semfreq,
         character2_semantic_family_size = semfamsize,
         character2_phonetic_component = phon, 
         character2_phonetic_component_freq = phonfreq,
         character2_phonetic_family_size = phonfam) %>%
  select(-freq:-phonfam) %>%
  left_join(cld.extracted.measures, by = c("simplified3" = "simp")) %>%
  mutate(character3_freq = freq,
         character3_family_size = famsize,
         character3_semantic_radical = semrad,
         character3_semantic_radical_freq = semfreq,
         character3_semantic_family_size = semfamsize,
         character3_phonetic_component = phon, 
         character3_phonetic_component_freq = phonfreq,
         character3_phonetic_family_size = phonfam) %>%
  select(-freq:-phonfam) %>%
  left_join(cld.extracted.measures, by = c("simplified4" = "simp")) %>%
  mutate(character4_freq = freq,
         character4_family_size = famsize,
         character4_semantic_radical = semrad,
         character4_semantic_radical_freq = semfreq,
         character4_semantic_family_size = semfamsize,
         character4_phonetic_component = phon, 
         character4_phonetic_component_freq = phonfreq,
         character4_phonetic_family_size = phonfam) %>%
  select(-freq:-phonfam) %>%
  distinct() -> chideod.finished.almost
```

# After shortly discussing with Arthur

```{r}
# the ASBC frequency measures as a separate list
# chideod.almost.finished %>%
#   mutate(language_stage = str_replace(language_stage, "MA", "SC")) %>%
#   select(traditional, contains("ASBC")) %>%
#   distinct() %>%
#   write_csv(here("interesting_lists", "ASBC_dp.csv"),
#             col_names = TRUE)
  

# without ASBC
chideod.almost.finished %>%
  mutate(language_stage = str_replace(language_stage, "MA", "SC")) %>%
  mutate(pinyin_without_tone = as.character(pinyin_without_tone)) %>%
  mutate(ipa_toneletter = as.character(ipa_toneletter)) %>%
  mutate(ipa_tonenumber = as.character(ipa_tonenumber)) %>%
  select(-contains("ASBC")) %>%
  distinct() -> chideod.finished

chideod.finished %>%
  count(sensory_imagery)
```



# FINAL OUTPUT

13 January 2020

```{r}
library(writexl)

chideod.finished %>%
  count(simplified)

write_rds(chideod.finished, here("revision", "chideod.revised.rds")) 
write_xlsx(chideod.finished, here("revision", "chideod.revised.xlsx"), col_names = TRUE) 
write_csv(chideod.finished, here("revision", "chideod.revised.csv"), col_names = TRUE) 

skimr::skim(chideod.finished)
```


