---
title: "Adding HYDC to CHIDEOD"
author: "Thomas Van Hoey"
date: "10/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(CHIDEOR)
#chideod 
library(tidyverse)
#hydc <- read_csv("/Users/Thomas/Google\ Drive/hydcd/hanyudacidian-csv.zip")
```

# Adding the language stage and recoding HYDC

```{r}
#chideod

chideod %>% 
  #top_n(50) %>%
  #select(traditional, HYDCD, datasource) %>%
  mutate(hanyu = case_when(nchar(HYDCD) > 0 ~ "HYDCD",
                           TRUE ~ "NA"
  )) %>%
  pivot_longer(cols = c(datasource, hanyu),
               names_to = "test") %>%
  filter(value != "NA") %>%
  rename(datasource = value) %>%
  select(-test) %>%
  mutate(datasource = case_when(
    datasource == "HYDCDmao-sheng" ~ "HYDCD",
    TRUE ~ datasource
  )) %>%
  distinct() %>%
  mutate(stage = case_when(
    datasource == "Gong" ~ "MA",
    datasource == "Li" ~ "MA",
    datasource == "Wang" ~ "MA",
    datasource == "Kroll" ~ "OC-MC",
    datasource == "Shijing" ~ "OC",
    datasource == "Tang" ~ "MC",
    datasource == "HYDCD" ~ "OC-MC-MA"
  )) %>%
  distinct() -> chideod.updated

chideod.updated

```

# Taking out ideophones based on Academia Sinica Balanced Corpus

Taking out some 'normal' words and words / compounds / interjections

```{r}
takeouts <- read_csv("post_procssing_filtering.csv") %>%
  filter(takeout == "Y")
takeouts

chideod.updated %>%
  anti_join(takeouts, by = c("traditional" = "word")) -> chideod.updated.takeout
```

# Adding frequencies and dispersion from Academia Sinica Balanced Corpus

From: post_processing.Rmd

```{r}
ASBC.ideo.dispersion.raw %>%
  rename(ASBC.philosophy = 哲學.y,
         ASBC.literature = 文學.y,
         ASBC.life = 生活.y,
         ASBC.society = 社會.y,
         ASBC.science = 科學.y,
         ASBC.art = 藝術.y,
         ASBC.dp = dp
  ) %>%
  select(ideo, contains("ASBC")) %>%
  replace(is.na(.), 0) -> ASBC.dp

chideod.updated.takeout %>%
  left_join(ASBC.dp, by = c("traditional" = "ideo")) -> chideod.updated.dp

```

# Recoding data type

```{r}
skimr::skim(chideod.updated.dp)
```



Problems:

* a number of character and double variables are coded as logical
* T4 and S4 have gone missing
* arrange according to number of characters (4, so it's easier at guessing coltypes)
* take out 5/6 character-ideophones
* 


```{r}
chideod.updated.dp %>%
  mutate(S4 = as.character(S4),
         T4 = as.character(T4),
         S4.sem = as.character(S4.sem),
         S4.phon = as.character(S4.phon)) %>%
  mutate_if(is.logical, as.double) %>%
    mutate(T4 = case_when(nchar(traditional) > 3 ~ str_extract(traditional, ".$"),
                          TRUE ~ T4),
           S4 = case_when(nchar(simplified) > 3 ~ str_extract(simplified, ".$"),
                          TRUE ~ S4)) %>%
  arrange(desc(nchar(traditional))) %>%
  filter(traditional != "呼嚕咕咚嗚隆" & 
           traditional != "得龍得龍咚" & 
           traditional != "落落落落噓") -> chideod.updated.4maximum

chideod.updated.4maximum %>%
  filter(str_detect(traditional, "ð")) %>% #these were corrupted, unicode problem
  write_csv("corrupted.ideophones.csv", col_names = TRUE)

chideod.updated.20191007 <- chideod.updated.4maximum %>%
  filter(!str_detect(traditional, "ð"))  #these were corrupted, unicode problem

chideod.updated.20191007
```

```{r}
write_csv(chideod.updated.20191007, "chideod.csv", col_names = TRUE)

library(writexl)
write_xlsx(chideod.updated.20191007, "chideod.xlsx", col_names = TRUE)

write_rds(chideod.updated.20191007, "chideod.rds")
```

